### 2016-09-30 architecture.tex
Better wording

As an example of the notions presented in this section,
Listing~\ref{fig:gamma-example} presents a minimal version of the gamma
function $\Gamma(x)$ from SymPy, which evaluates itself on positive integer
arguments, has the real assumption defined, can be rewritten in
terms of factorial with \verb|gamma(x).rewrite(factorial)|, and can be
differentiated. \texttt{self.func} is used throughout
instead of referencing \texttt{gamma} explicitly so that potential subclasses
of \texttt{gamma} can reuse the methods.

>>>>

Listing~\ref{fig:gamma-example} presents an example of extensibility in SymPy.
It gives a minimal version of the gamma function $\Gamma(x)$ from SymPy, which
evaluates itself on positive integer arguments, has the real assumption
defined, can be rewritten in terms of factorial with
\verb|gamma(x).rewrite(factorial)|, and can be differentiated.
\texttt{self.func} is used throughout instead of referencing \texttt{gamma}
explicitly so that potential subclasses of \texttt{gamma} can reuse the
methods.
